|

### 2022-06-23 docs/rmd/paper.Rmd
autogit

---
title: |
  <center>Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression: </center>
  <center>
    A comparison of $\epsilon$-Lexicase Selection and Tournament Selection
  </center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Research Project for Seminar Information Systems (03.996.3299)</center>
  <center>Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  <center>Summerterm 2022</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  pdf_document:
    keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: settings.tex
# indent: true
fontsize: 12pt
# toc: yes
# toc_depth: 4
bibliography: bib/bib/ref.bib
csl: bib/csl/harvard1.csl
# include-before: '`\newpage{} `{=latex}'
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

All GP experiments will be implemented by using the python programming language in conjunction with DEAP, a framework for distributed evolutionary algorithms that implements various tools and algorithms for genetic programming [@DEAP_JMLR2012].

@@

In a final step I analyze the growth behavior for both GP systems to determine if differences in program size can be observed based on selection operators. Figure 3 visualizes the average size of individuals inside the population as well as the average size of the best performing individual for each generation and both GP systems. 
![Mean Size](./plots/size_subplotted.png)

@@

@@

```{zsh github, include=FALSE}
git add * && git commit --m "rendered doc" && git push
```

>>>>

---
title: |
  <center>Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression: </center>
  <center>
    A comparison of $\epsilon$-Lexicase Selection and Tournament Selection
  </center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Research Project for Seminar Information Systems (03.996.3299)</center>
  <center>FB 03: Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  <center>Summerterm 2022</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  pdf_document:
    keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: settings.tex
# indent: true
fontsize: 12pt
# toc: yes
# toc_depth: 4
bibliography: bib/bib/ref.bib
csl: bib/csl/harvard1.csl
# include-before: '`\newpage{} `{=latex}'
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

All GP experiments will be implemented by using the python programming language in conjunction with DEAP, a framework for distributed evolutionary algorithms that implements various tools and algorithms for genetic programming [@DEAP_JMLR2012]. A github repository that contains the full source code, tables, plots and other materials represented in this thesis can be accessed at [https://github.com/roman91DE/intelligent_information_systems_research_project](#https://github.com/roman91DE/intelligent_information_systems_research_project).

@@

In a final step I analyze the growth behavior for both GP systems to determine if differences in program size can be observed based on selection operators. Figure 3 visualizes the average size of individuals inside the population as well as the average size of the best performing individual for each generation and both GP systems. 
\begin{figure}
\centering
\includegraphics{./plots/size_subplotted.png}
\caption{Mean Size}
\end{figure}

<!-- ![Mean Size](./plots/size_subplotted.png)--->

@@

...

@@

### 2022-06-23 docs/rmd/paper.tex
autogit

Chair of Business Administration and Computer Science

@@

All GP experiments will be implemented by using the python programming
language in conjunction with DEAP, a framework for distributed
evolutionary algorithms that implements various tools and algorithms for
genetic programming (Fortin \emph{et al.}, 2012).

@@

In a final step I analyze the growth behavior for both GP systems to
determine if differences in program size can be observed based on
selection operators. Figure 3 visualizes the average size of individuals
inside the population as well as the average size of the best performing
individual for each generation and both GP systems.
\includegraphics{./plots/size_subplotted.png}

@@

>>>>

FB 03: Chair of Business Administration and Computer Science

@@

All GP experiments will be implemented by using the python programming
language in conjunction with DEAP, a framework for distributed
evolutionary algorithms that implements various tools and algorithms for
genetic programming (Fortin \emph{et al.}, 2012). A github repository
that contains the full source code, tables, plots and other materials
represented in this thesis can be accessed at
\protect\hyperlink{https:ux2fux2fgithub.comux2froman91DEux2fintelligent_information_systems_research_project}{https://github.com/roman91DE/intelligent\_information\_systems\_research\_project}

@@

In a final step I analyze the growth behavior for both GP systems to
determine if differences in program size can be observed based on
selection operators. Figure 3 visualizes the average size of individuals
inside the population as well as the average size of the best performing
individual for each generation and both GP systems.

\begin{figure}
\centering
\includegraphics{./plots/size_subplotted.png}
\caption{Mean Size}
\end{figure}

@@

\ldots{}
